### 2020-04-08 paper/paper.tex
Some progress...

% \documentclass[sigconf,natbib=false,authordraft]{acmart}
\documentclass[sigconf,natbib=false]{acmart}

% References
\usepackage[style=ACM-Reference-Format,backend=bibtex,sorting=none]{biblatex}
\addbibresource{references.bib}

\usepackage{booktabs}

% ACM License Text
\setcopyright{acmcopyright}

% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

% Conference Details
% \acmConference[WOODSTOCK'19]{ACM Woodstock conference}{July 2019}{El Paso, Texas USA}

% Year
\acmYear{2020}

% Copyright Year
\copyrightyear{2020}

\title{Comparison of CORD-19-trained GPT-2-based Chatbot Responses Across
  Different Text Semantic Similarity Approaches}

\author{David Oniani}
\affiliation{%
  \institution{Mayo Clinic}
  \city{Rochester}
  \state{MN}
  \country{USA}}
\email{oniani.david@mayo.edu}

\author{Dr.~Yanshan Wang}
\affiliation{%
  \institution{Mayo Clinic}
  \city{Rochester}
  \state{MN}
  \country{USA}}
\email{wang.yanshan@mayo.edu}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

  On March 16 (2020), per request of the White House Office of Science and
  Technology Policy, new COVID-19 machine readable dataset
  (CORD-19)~\cite{whitehousecovid2020} has been released. We have utilized 774M
  GPT-2~\cite{radford2019language} model and applied transfer learning to
  retrain the model on this corpus. Ultimately, we have created a COVID-19
  conversational chatbot. In order to improve the performance of the chatbot,
  we have applied 4 different text semantic similarity techniques using
  pretrained models including BERT~\cite{turc2019}, BioBERT~\cite{btz682}, and
  Universal Sentence Encoder (USE)~\cite{use} as additional layers on top of
  GPT-2-based chatbot responses. We present the results annotated by
  experienced medical personnel at Mayo Clinic.

\end{abstract}

\keywords{gpt-2, covid-19, cord-19, bert, biobert, universal sentence encoder,
  dataset, nlp, ai, semantic similarity}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Chatbots have been much studied in recent years and with the advancements in
the fields of artificial intelligence and natural language processing, both the
the functionality and the performance of these tools have seen drastic
improvements. Semantic similarity of texts, on the other hand, has been studied
for a long time and recent breakthroughs allowed employing it for a better
classification. The paper takes an approach which is really a marriage of these
two and brings a different perspective on the chatbot creation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dataset and Model
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Dataset}

We harvested the data from the initial \textit{commercial use subset} of
COVID-19 Open Research Dataset (CORD-19)~\cite{cord19} containing 9000
scholarly articles in the form of JSON files. We extracted the abstract and the
main body of the article from every JSON file, combined them together, and used
as a corpus for retraining the GPT-2 model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Transfer Learning
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Transfer Learning}

We used GPT-2 774M model and ran transfer learning for 2500 iterations with the
batch size of 8. We used Adam as the optimizer and set the learning rate of
0.0001. The model is available on our GitHub page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Semantic Similarity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Semantic Similarity}

The GPT-2 responses are usually very lengthy and for the most part, the answer
is not relevant to the question. To solve this problem, we chunked the answer
into separate sentences and found the ones that are most \textit{semantically
  similar} to the question asked. For this task, we have applied 4 different
approaches:

\begin{itemize}
  \item BioBERT large v1.1 (+PubMed 1M) model based on BERT-large Cased (custom 30k vocabulary)
  \item Universal Sentence Encoder Version 3, large
  \item Bert-Large, uncased with 24 layers and 340M parameters
  \item Scikit learn's cosine similarity
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

We have generated over 300 answers to the questions. We have asked experienced
medical personnel at Mayo Clinic to rate our question.

\begin{figure}[H]
  \centering
  \begin{tabular}{*{2}{c}}
    \toprule
    Approach & Score\\
    \midrule
    TfidfVectorizer + Cosine Similarity & TBD\\
    \midrule
    BERT + Cosine Similarity & TBD\\
    \midrule
    BioBERT + Cosine Similarity & TBD\\
    \midrule
    Universal Sentence Encoder (USE) + Inner Product & TBD\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of 4 Different Approaches.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean porta purus et
sem gravida rutrum. Maecenas blandit nulla ac luctus tempus. Nam finibus
posuere ante, et lacinia massa vestibulum sit amet. Nulla velit arcu, efficitur
quis turpis nec, sollicitudin lobortis nisi. Vivamus ut diam ut eros faucibus
fringilla. Suspendisse pellentesque magna nec velit tristique sollicitudin.
Morbi ultrices nec augue et molestie. Nam sapien ante, ullamcorper elementum
convallis id, faucibus in lectus. Fusce pellentesque mollis velit efficitur
porta. Sed finibus ligula quam, et lacinia velit posuere auctor. Donec ligula
lorem, dictum nec lectus in, vehicula tincidunt massa. In hac habitasse platea
dictumst.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\printbibliography%

\end{document}

### 2020-04-08 paper/paper.tex
Small improvements to the prose

@@
 the fields of artificial intelligence and natural language processing, both the
-the functionality and the performance of these tools have seen drastic
-improvements. Semantic similarity of texts, on the other hand, has been studied
-for a long time and recent breakthroughs allowed employing it for a better
-classification. The paper takes an approach which is really a marriage of these
-two and brings a different perspective on the chatbot creation.
+the functionality and the performance have seen drastic improvements. Semantic
+similarity of texts, on the other hand, has been studied for a long time and
+recent breakthroughs allowed for development of new models such as BERT,
+BioBERT, and Universal Sentence Encoder. The paper takes an approach which is a
+marriage of these two and brings a different perspective on the chatbot
+creation. We first let a human ask a question and make GPT-2 come up with an
+answer. Then we further process the answer with additional filters and
+ultimately, apply a different model for finding the sentences that are most
+relevant to the question.
 
@@
 
-\section{Dataset}
+\section{Corpus}
 
@@
 into separate sentences and found the ones that are most \textit{semantically
-  similar} to the question asked. For this task, we have applied 4 different
-approaches:
+  similar} to the question asked. For this task, we have tested and applied 4
+different approaches:
 
@@
   \item BioBERT large v1.1 (+PubMed 1M) model based on BERT-large Cased (custom 30k vocabulary)
-  \item Universal Sentence Encoder Version 3, large
-  \item Bert-Large, uncased with 24 layers and 340M parameters
-  \item Scikit learn's cosine similarity
+  \item Universal Sentence Encoder (USE), version 3, large
+  \item Bert-Large, uncased (24 layers and 340M parameters)
+  \item Scikit learn's Tfidfvectorizer
 \end{itemize}

### 2020-04-08 paper/paper.tex
Update repository

@@
 
-We used GPT-2 774M model and ran transfer learning for 2500 iterations with the
-batch size of 8. We used Adam as the optimizer and set the learning rate of
+We utilized GPT-2 774M model and ran transfer learning for 2500 iterations with
+the batch size of 8. We used Adam as the optimizer and set the learning rate of
 0.0001. The model is available on our GitHub page.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Questions and Evaluation
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Questions}
+
+For evaluating the performance of the approaches, we have chose 12 different
+questions. For each approach, we generated 5 different answers for the same
+question, resulting in the total of 240 answers. We then asked experienced
+medical personnel at Mayo Clinic to rate these answers. The questions are
+presented below.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Results
@@
 \section{Results}
-
-We have generated over 300 answers to the questions. We have asked experienced
-medical personnel at Mayo Clinic to rate our question.
 

### 2020-04-11 paper/paper.tex
Fix incomplete questions and update the paper

@@
 
-\section{Questions}
+\section{Questions and Evaluation}
 
-For evaluating the performance of the approaches, we have chose 12 different
+For evaluating the performance of the approaches, we chose 12 different
 questions. For each approach, we generated 5 different answers for the same
@@
 presented below.
+
+\begin{itemize}
+  \item Are there geographic variations in the mortality rate of COVID-19?
+  \item What is known about transmission, incubation, and environmental stability of COVID-19?
+  \item Is there any evidence to suggest geographic based virus mutations of COVID-19?
+  \item Are there geographic variations in the rate of COVID-19 spread?
+  \item What do we know about virus genetics, origin, and evolution of COVID-19?
+  \item What has been published about ethical and social science considerations of COVID-19?
+  \item What has been published about medical care of COVID-19?
+  \item What do we know about diagnostics and surveillance of COVID-19?
+  \item What do we know about COVID-19 risk factors?
+  \item What has been published about information sharing and inter-sectoral collaboration of COVID-19?
+  \item What do we know about vaccines and therapeutics of COVID-19?
+  \item What do we know about non-pharmaceutical interventions of COVID-19?
+\end{itemize}
 

### 2020-04-11 paper/paper.tex
Added annotation guidelines

@@
 For evaluating the performance of the approaches, we chose 12 different
-questions. For each approach, we generated 5 different answers for the same
-question, resulting in the total of 240 answers. We then asked experienced
-medical personnel at Mayo Clinic to rate these answers. The questions are
-presented below.
+questions (presented below).
 
@@
   \item Are there geographic variations in the mortality rate of COVID-19?
-  \item What is known about transmission, incubation, and environmental stability of COVID-19?
-  \item Is there any evidence to suggest geographic based virus mutations of COVID-19?
+
+  \item What is known about transmission, incubation, and environmental
+        stability of COVID-19?
+
+  \item Is there any evidence to suggest geographic based virus mutations of
+        COVID-19?
+
   \item Are there geographic variations in the rate of COVID-19 spread?
-  \item What do we know about virus genetics, origin, and evolution of COVID-19?
-  \item What has been published about ethical and social science considerations of COVID-19?
+
+  \item What do we know about virus genetics, origin, and evolution of
+        COVID-19?
+
+  \item What has been published about ethical and social science considerations
+        of COVID-19?
+
   \item What has been published about medical care of COVID-19?
+
   \item What do we know about diagnostics and surveillance of COVID-19?
+
   \item What do we know about COVID-19 risk factors?
-  \item What has been published about information sharing and inter-sectoral collaboration of COVID-19?
+
+  \item What has been published about information sharing and inter-sectoral
+        collaboration of COVID-19?
+
   \item What do we know about vaccines and therapeutics of COVID-19?
+
   \item What do we know about non-pharmaceutical interventions of COVID-19?
+\end{itemize}
+
+\noindent For each approach, we generated 5 different answers for the same
+question, resulting in the total of 240 answers. We then asked experienced
+medical personnel at Mayo Clinic to rate these answers. The rating system was
+composed of 5 different scores:
+
+\begin{itemize}
+  \item	Relevant --- the answer partially or fully answers the question and/or
+        makes clear attempts to do so and is related to the question.
+        (5 points)
+
+  \item	Well-formed --- the answer makes a logical sense and is somewhat
+        related to both the question and COVID-19, yet it does not (partially
+        or fully) answer the question.
+        (4 points)
+
+  \item	Informative --- the answer is not related to the question, but provides
+        some information about COVID-19 and makes a logical sense.
+        (3 points)
+
+  \item	Acceptable --- the answer makes some logical sense and is weakly
+        related to the question or COVID-19, but is mostly difficult to
+        understand.
+        (2 points)
+
+  \item	Poor --- the answer is totally unrelated to the question or COVID-19
+        and/or does not make a logical sense.
+        (1 point)
 \end{itemize}

### 2020-04-20 annotations/iaa.py
Update repository

@@ -1,0 +1,27 @@
+#!/usr/bin/env python3
+# encoding: UTF-8
+
+"""
+Filename: iaa.py
+Author:   David Oniani
+E-mail:   oniani.david@mayo.edu
+
+Description:
+    Reports metrics for Inner Annotation Agreement (IAA).
+"""
+
+import numpy as np
+
+from sklearn import metrics
+
+
+if __name__ == "__main__":
+    annotator_1 = [3, 3, 1, 1, 5, 4, 5, 3, 2, 2, 1, 5, 4, 4, 4, 3, 4, 3, 4, 4]
+    annotator_2 = [1, 5, 4, 4, 5, 2, 4, 3, 5, 1, 2, 5, 4, 5, 5, 3, 5, 4, 5, 4]
+
+    print(
+        "Cohen's Kappa:", metrics.cohen_kappa_score(annotator_1, annotator_2)
+    )
+    print(
+        "Correlation Coefficient:", np.corrcoef(annotator_1, annotator_2)[0][1]
+    )

### 2020-04-23 annotations/annotation_guidelines/annotation_guidelines.tex
Small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Filename: annotation_guidelines.tex
% Author:   David Oniani
% Modified: April 02, 2020
%  _         _____   __  __
% | |    __ |_   _|__\ \/ /
% | |   / _` || |/ _ \\  /
% | |__| (_| || |  __//  \
% |_____\__,_||_|\___/_/\_\
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Definition
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages and Related Settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Global, document-wide settings
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Other packages
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[cache=false]{minted}
\usepackage{tocloft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Command Definitions and Redefinitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% New commands
\newcommand{\rarr}{\rightarrow}             % Leftarrow
\newcommand{\larr}{\leftarrow}              % Rightarrow
\newcommand\und[1]{\underline{\smash{#1}}}  % Nice-looking underline
\renewcommand{\baselinestretch}{1.5}        % Line spacing is 1.5

% Rename "Contents" to "Table of Contents"
\addto\captionsenglish{% Replace "english" with the language used
  \renewcommand{\contentsname}%
    {\textbf{Table of Contents}}}%

% Filling the space for centering the title of the table of contents
% Dots for ToC sections
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cfttoctitlefont}{\hspace*{\fill}\Large}
\renewcommand{\cftaftertoctitle}{\hspace*{\fill}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Miscellaneous
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Setting stuff
\setlength{\parindent}{0pt}  % Remove indentations from paragraphs
\pagestyle{fancy}            % This allows to do fancy headers and footers
\fancyhf{}                   % No additional page numbering (or other stuff)
\cfoot{\thepage}             % Display page number at the bottom, in the center

% PDF information and nice-looking urls
\hypersetup{%
  pdfauthor={David Oniani},
  pdftitle={Annotation Guidelines for COVID-19 Chatbot},
  pdfsubject={COVID-19, Aritificial Intelligence, Mayo Clinic},
  pdfkeywords={COVID-19, Aritificial Intelligence, Mayo Clinic},
  pdflang={English},
  colorlinks=true,
  linkcolor={black!50!blue},
  citecolor={black!50!blue},
  urlcolor={black!50!blue}
}

% Put a centered header of a footnote size on the top of each page
\lhead{\footnotesize{Annotation Guidelines for COVID-19 Chatbot}}
\rhead{\footnotesize{David Oniani and Dr.~Yanshan Wang}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author(s), Title, and Date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Author(s)
\author{David Oniani\\
        Mayo Clinic\\
        \href{mailto:oniani.david@mayo.edu}{mailto:oniani.david@mayo.edu}
        \and
        Dr.~Yanshan Wang\\
        Mayo Clinic\\
        \href{mailto:wang.yanshan@mayo.edu}{mailto:wang.yanshan@mayo.edu}}

% Title
\title{\textbf{Annotation Guidelines for COVID-19 Chatbot}}

% Date
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beginning of the Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Question Categorization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Answer Categorization}

Answers will be categorized according to 5 categories:

\begin{itemize}
  \item	Relevant -- the answer partially or fully answers the question and/or
        makes clear attempts to do so and is related to the question.
        (5 points)

  \item	Well-formed -- the answer makes a logical sense and is somewhat related
        to both the question and COVID-19, yet it does not (partially or fully)
        answer the question.
        (4 points)

  \item	Informative -- the answer is not related to the question, but provides
        some information about COVID-19 and makes a logical sense.
        (3 points)

  \item	Acceptable -- the answer makes some logical sense and is weakly related
        to the question or COVID-19, but is mostly difficult to understand.
        (2 points)

  \item	Poor -- the answer is totally unrelated to the question or COVID-19
        and/or does not make a logical sense.
        (1 point)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Example Answers and Evaluation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Example Answers and Evaluation}

The answers below are made-up and are not present in the actual evaluation
data.

\subsection{Relevant (5 Points)}

Question: Are there geographic variations in the mortality rate of COVID-19?

\textbf{Answer}: \textit{The mortality rate of COVID-19 depends on the
geography a lot and some places in the world might be more vulnerable to it
than others. It is also important to consider other causes. I love ice cream!}

\medskip

Explanation: The answer would be rated 5 since it is clearly related to the
question. Although the answer mentions unrelated bits like ``I love ice
cream'', it is mostly relevant to the question.

\subsection{Well-formed (4 Points)}

Question: Are there geographic variations in the mortality rate of COVID-19?

\textbf{Answer}: \textit{Geography is a great subject! You should learn it!
Also, COVID-19 has been tough geographically. It is terrible if you get it.}

\medskip

Explanation: The answer is somewhat related to the question since it mentions
both the geography and COVID-19, however, it does not answer the question.

\subsection{Informative (3 Points)}

Question: Are there geographic variations in the mortality rate of COVID-19?

\textbf{Answer}: \textit{COVID-19 or Novel coronavirus is a threat to human
health. It is bad if you get it so be safe. Some scientists think that it
spreads faster than Influenza.}

\medskip

Explanation: Although the text is not directly related the question, it
provides some information about COVID-19 and makes a logical sense.

\subsection{Acceptable (2 Point)}

Question: Are there geographic variations in the mortality rate of COVID-19?

\textbf{Answer}: \textit{Some disease are viral. There has been viral diseases
recently. It can be damaging to people.}

\medskip

Explanation: The answer is weakly related to COVID-19 since it mentions terms
``disease'' and ``viral.'' Yet, it fails to deliver the answer related to
COVID-19 or the question.

\subsection{Poor (1 Point)}

Question: Are there geographic variations in the mortality rate of COVID-19?

\textbf{Answer}: \textit{To be, or not to be, that is the question???! What is
life? What is Earth? What is human? Soma animals are carnivores and some are
herbivores, and some omnivores.}

\medskip

Explanation: The answer is totally unrelated to the question or COVID-19.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The End of the Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2020-04-24 results/220_answers_left.py
Left to annotate

@@ -1,0 +1,81 @@
+#!/usr/bin/env python3
+# encoding: UTF-8
+
+"""
+Filename: 220_answers_left.py
+Author: David Oniani
+E-mail: oniani.david@mayo.edu
+
+Description:
+    Filter out 220 answers that have to be annotated.
+"""
+
+import csv
+
+import pandas as pd
+
+
+def main() -> None:
+    """The main function."""
+
+    # Process the data
+    answers_all = pd.read_csv("answers_all.csv")
+    answers_temp = pd.read_csv("answers_post_annotation.csv")
+    answers_post_annotation = pd.DataFrame(
+        {
+            "Question": answers_temp["Question"],
+            "Answer": answers_temp["Answer"],
+            "Approach": answers_temp["Approach"],
+        }
+    )
+
+    rows_all = []
+    for _, row in answers_all.iterrows():
+        rows_all.append((row[0], row[1], row[2]))
+
+    rows_post_annotation = []
+    for _, row in answers_post_annotation.iterrows():
+        rows_post_annotation.append((row[0], row[1], row[2]))
+
+    # Filter out the answers
+    left = []
+    for answer in rows_all:
+        if answer not in rows_post_annotation:
+            left.append(answer)
+
+    # Write the data to the CSV file
+    with open("left_to_annotate.csv", "w") as csv_file:
+        writer = csv.writer(csv_file, delimiter=",")
+        # The header
+        writer.writerow(
+            [
+                "Question",
+                "Answer",
+                "Answer Category - Relevant?",
+                "Answer Category - Well-formed?",
+                "Answer Category - Informative?",
+                "Answer Category - Acceptable?",
+                "Answer Category - Poor?",
+                "Answer Relevance (1-5)",
+                "Approach",
+            ]
+        )
+
+        for question, answer, approach in left:
+            writer.writerow(
+                [
+                    question,
+                    answer,
+                    "Answer Category - Relevant?",
+                    "Answer Category - Well-formed?",
+                    "Answer Category - Informative?",
+                    "Answer Category - Acceptable?",
+                    "Answer Category - Poor?",
+                    "Answer Relevance (1-5)",
+                    approach,
+                ]
+            )
+
+
+if __name__ == "__main__":
+    main()

### 2020-04-24 results/answers_left.py
Left to annotate

@@ -2,12 +2,12 @@
 # encoding: UTF-8
 
 """
-Filename: 220_answers_left.py
+Filename: answers_left.py
 Author: David Oniani
 E-mail: oniani.david@mayo.edu
 
 Description:
-    Filter out 220 answers that have to be annotated.
+    Generate the file with the answers that are left to be annotated.
 """
 
 import csv
@@ -63,17 +63,7 @@ def main() -> None:
 
         for question, answer, approach in left:
             writer.writerow(
-                [
-                    question,
-                    answer,
-                    "Answer Category - Relevant?",
-                    "Answer Category - Well-formed?",
-                    "Answer Category - Informative?",
-                    "Answer Category - Acceptable?",
-                    "Answer Category - Poor?",
-                    "Answer Relevance (1-5)",
-                    approach,
-                ]
+                [question, answer, "", "", "", "", "", "", approach,]
             )
 
 

### 2020-05-26 paper/paper.tex
Update repository

--- 2020-04-08 paper/paper.tex
@@
 \usepackage{booktabs}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+\tikzstyle{item} = [rectangle, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=gray!50]
+\tikzstyle{arrow} = [thick,->,>=stealth,shorten <= 1.5pt,shorten >= 1.5pt]
 
@@
   \institution{Mayo Clinic}
+  \department{Kern Center for the Science of Health Care Delivery}
   \city{Rochester}
@@
   \institution{Mayo Clinic}
+  \department{Division of Digital Health Sciences}
   \city{Rochester}
@@
 \begin{abstract}
-
 On March 16 (2020), per request of the White House Office of Science and
 Technology Policy, new COVID-19 machine readable dataset
-  (CORD-19)~\cite{whitehousecovid2020} has been released. We have utilized 774M
-  GPT-2~\cite{radford2019language} model and applied transfer learning to
-  retrain the model on this corpus. Ultimately, we have created a COVID-19
-  conversational chatbot. In order to improve the performance of the chatbot,
-  we have applied 4 different text semantic similarity techniques using
-  pretrained models including BERT~\cite{turc2019}, BioBERT~\cite{btz682}, and
-  Universal Sentence Encoder (USE)~\cite{use} as additional layers on top of
-  GPT-2-based chatbot responses. We present the results annotated by
-  experienced medical personnel at Mayo Clinic.
+(CORD-19)~\cite{whitehousecovid2020} has been released. Yet, there still was a
+need for making this dataset more interpretable and understandable for the
+general audience. Besides, there was an urgent need of fast and efficient
+information exchange. To accomplish this goal, we built an interactive chatbot
+that answers questions related to COVID-19. This not only made the information
+from the CORD-19 dataset more understandable to the general audience, but also
+put it into real-world use and helped efficiently obtain information concerning
+COVID-19. We have utilized 774M GPT-2~\cite{radford2019language} model and
+applied transfer learning to retrain the model on the CORD-19 corpus.
+Ultimately, we have created an interactive COVID-19 conversational chatbot. In
+order to improve the performance of the chatbot, we have applied 4 different
+text semantic similarity techniques using pre-trained models including
+BERT~\cite{turc2019}, BioBERT~\cite{btz682}, and Universal Sentence Encoder
+(USE)~\cite{use} as layers on top of GPT-2-based chatbot. For performance
+evaluation purposes, we have asked experienced personnel at Mayo Clinic to rate
+our answers and also present these annotations in the paper. Additionally, we
+have created a user-friendly interactive web application to be hosted online
+and made available for anyone to get more information regarding COVID-19. Our
+work has produced good results in both designing a chatbot that produces
+high-quality answers to COVID-19-related questions (hence, improving COVID-19
+information exchange) and comparing the performance of several embedding
+generation and vectorization techniques in the biomedical domain.
 
@@
 
-\keywords{gpt-2, covid-19, cord-19, bert, biobert, universal sentence encoder,
+\keywords{gpt-2, covid-19, cord-19, bert, biobert, universal sentence encoder, tf-idf
   dataset, nlp, ai, semantic similarity}
@@
 
-Chatbots have been much studied in recent years and with the advancements in
-the fields of artificial intelligence and natural language processing, both the
-the functionality and the performance have seen drastic improvements. Semantic
+COVID-19/Novel coronavirus is an infectious disease caused by severe acute
+respiratory syndrome coronavirus 2 (SARS-CoV-2). It was first identified in
+December of 2019 in Wuhan, China, and has since spread globally, resulting in
+an unprecedented pandemic. As of 17 May 2020, more than 4.66 million cases have
+been reported across 188 countries and territories, resulting in more than
+312,000 deaths. The White House Office of Science and Technology Policy has
+requested a COVID-19 machine readable dataset, now known as CORD-19. Since its
+rapid emergence started, many countries have declared the state of emergency
+and the need for fast and efficient information sharing as well as tracking
+progress related to COVID-19 became crucial. For addressing these issues, we
+decided to use CORD-19 for designing a chatbot that would answer questions
+related to COVID-19. The chatbot would not only help improve information
+sharing, but also as a knowledge base for COVID-19.
+
+\bigskip
+
+\noindent A chatbot is a software which is able to conduct a conversation via
+text and/or other means. It is designed to emulate the way people communicate
+and give a sense that the conversation only involves humans. Therefore, cutting
+edge chatbots can hold a human-level conversation and usually, the performance
+of the chatbot is measured via the quality of its responses to humans. Chatbots
+have been much studied in recent years and with the advancements in the fields
+of artificial intelligence (AI) and natural language processing (NLP), both the the
+functionality and the performance have seen drastic improvements. Semantic
 similarity of texts, on the other hand, has been studied for a long time and
 recent breakthroughs allowed for development of new models such as BERT,
-BioBERT, and Universal Sentence Encoder. The paper takes an approach which is a
-marriage of these two and brings a different perspective on the chatbot
-creation. We first let a human ask a question and make GPT-2 come up with an
-answer. Then we further process the answer with additional filters and
-ultimately, apply a different model for finding the sentences that are most
-relevant to the question.
+BioBERT, and Universal Sentence Encoder. Today, one of the state-of-the art
+conversational artificial intelligence models is GPT-2. GPT-2 is a pre-trained
+model, so we have applied transfer learning utilizing CORD-19 for retraining
+purposes. The resulted chatbot gave irregularly long responses that would not
+be typical of a human. We have therefore decided to further filter the
+responses via applying embedding generation algorithms and models such as
+tf-idf, BERT, BioBERT, and Universal Sentence Encoder (USE) and then using
+semantic similarity approaches such as cosine similarity and inner product. In
+other words, we first let a human ask a question and make GPT-2 come up with an
+answer. We the further processed the response` with additional filters and
+ultimately, applied an embedding generation model for finding the sentences
+that are most relevant to the question.
+
+\bigskip
+
+\noindent Our study has produced a chatbot that is both performant and
+extensible. Additional layer of filters have shown success in classifying
+sentences. The chatbot is also able to be retrained and readjusted to new data,
+in case there are new discoveries and scientific achievements related to
+COVID-19. Furthermore, chatbot responses have been annotated by experienced
+staff at Mayo Clinic and the resuts were consistent across the annotators.
+
+\bigskip
+
+\noindent We will proceed by discussing the related work and the efforts that
+have been made previously. A few sections will be dedicated to specific
+approaches and materials used in this work. We will discuss the chatbot
+evaluation strategy as well as present the annotation results. Finally, we will
+also discuss the web-based tool designed to be used with this chatbot the
+source code of which (alongside with everything discussed) has been made
+available online.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Related Work
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Related Work}
+
+In the GPT-2 domain, some efforts were made by Wang et al.~\cite{gpt2-ad} where GPT-2
+was retrained in order to automatically generate answers to AD-related consumer
+questions posted by caregivers and evaluate how good  AI is at answering those
+questions. Lee and Hsiang~\cite{lee-hsiang} have fine-tuned GPT-2 for
+generating patent claims.  Klein and Nabi~\cite{klein-nabi} have applied GPT-2
+in conjunction with BERT for automatic questin generation purposes. We are
+unaware of the work which applied 775M GPT-2 model for transfer learning
+purposes on the CORD-19 dataset.
+
+\bigskip
+
+\noindent In regard to the work related to comparing pre-trained AI models,
+Jin et al. have made some efforts conducting probing experiments and comparing
+BERT, ELMo~\cite{elmo}, and BioBERT. Sharma and Daniel~\cite{bioflair} compared
+the performance of BERT networks to that of FLAIR~\cite{akbik2018coling}.
+
+\bigskip
+
+\noindent In the general artificial intelligence based chatbot domain, Serbal et al.
+~\cite{reinforce-chatbot} have applied deep reinforcement learning for building a
+conversational AI chatbot. Adiwardana et al.~\cite{toward-human-chatbot} have developed
+a multi-turn open-domain chatbot trained end-to-end on data mined social media conversations.
+Yin et al.~\cite{therapy-chatbot} have developed a deep learning based chatbot for
+psychological therapy purposes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Materials
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Materials}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Corpus}
 
@@
 
-\section{Transfer Learning}
+\section{Methods}
+
+We applied a hybrid approach for generating responses. The answer for the
+question first gets generated by GPT-2. Then some filtering is done by handling
+irregular patterns, extra spaces, and redundant punctuation. Additional
+filtering is done by leaving only the sentences that are most semantically
+similar to the question, usually eliminating a large portion of the response
+that would otherwise still be present and potentially make the response
+confusing. Such hybrid approach to the response generation produced high
+quality responses to COVID-19-related questions. Figure 1 illustrates this
+approach.
+
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}[node distance=2cm]
+    \node (human)        [item]                     {Human};
+    \node (chatbot)      [item, below of=human]     {GPT-2-based Chatbot};
+    \node (filtering)    [item, below of=chatbot]   {Filtering Based on Regex/String
+      Manipulation};
+    \node (filtering-ss) [item, below of=filtering] {Filtering Based on Semantic
+      Similarity to the Question};
+    \node (final)     [item, below of=filtering-ss] {Final Response};
+
+    \draw [arrow] (human)        -- node[anchor=west] {Question}          (chatbot);
+    \draw [arrow] (chatbot)      -- node[anchor=west] {Response}          (filtering);
+    \draw [arrow] (filtering)    -- node[anchor=west] {Filtered Response} (filtering-ss);
+    \draw [arrow] (filtering-ss) -- node[anchor=west] {Filtered Response} (final);
+  \end{tikzpicture}
+  \caption{Response Generation.}
+\end{figure}
+
+\subsection{Transfer Learning}
 
 We utilized GPT-2 774M model and ran transfer learning for 2500 iterations with
-the batch size of 8. We used Adam as the optimizer and set the learning rate of
-0.0001. The model is available on our GitHub page.
+the batch size of 8. We used Adam~\cite{adam} as the optimizer and set the
+learning rate of 0.0001. The link for downloading the model is available on our
+GitHub page.
+
+\bigskip
+
+\noindent GPT-2 has a Transformer~\cite{vaswani} based architecture which, in
+many ways, is similar to Open AI GPT model\cite{radford2019language}\cite{gpt}.
+There are 4 different versions of GPT-2. It features models with 124 million,
+355 million, 774 million, and 1.5 billion parameters. We have utilized the
+version with 774 million parameters. The original GPT-2 was written in
+tensorflow~\cite{tensorflow2015-whitepaper} and this is the version we have
+used. That said, for retraining purposes, we have utilized the TPU-trainable
+version of the GPT-2~\cite{gpt-2-tpu}.
+
+\bigskip
+
+\noindent Adam an algorithm for first-order gradient-based optimization of
+stochastic objective functions, based on adaptive estimates of lower-order
+moments~\cite{adam}. It is highly memory-efficient and has shown good results
+in retraining our chatbot. We have also tried SGD~\cite{SGD}, yet Adam has
+shown a better performance and therefore, we have released the Adam-based
+GPT-2 retrained model.
+
+\bigskip
+
+\noindent For building a web interface for our chatbot, we have used Python's
+package flask~\cite{flask} and integrated it with tensorflow. This resulted
+in a simple and user-friendly user interface.
 
@@
 
-\section{Semantic Similarity}
+\subsection{Semantic Similarity}
 
-The GPT-2 responses are usually very lengthy and for the most part, the answer
-is not relevant to the question. To solve this problem, we chunked the answer
-into separate sentences and found the ones that are most \textit{semantically
-  similar} to the question asked. For this task, we have tested and applied 4
-different approaches:
+Semantic similarity is a metric that quantifies the degree to which two texts
+or text documents are similar to each other. The two approaches we have used
+include cosine similarity and inner product. We used these approaches as an
+additional layer to the language model.
+
+\bigskip
+
+\noindent Cosine similarity is one of the most commonly used approaches in
+calculating semantic similarity of texts. Therefore, it is naturally employed
+in natural language processing tasks. Many NLP applications need to
+compute the semantic similarity between two short texts. Its flexibility allows
+one to apply it under virtually any settings, as long as documents can be
+represented as vectors.  Besides, finding cosine similarity is usually not a
+time-consuming task and can be done really quickly. Therefore, it is also commonly
+used for benchmarking purposes~\cite{cosine-benchmark}.
+
+\bigskip
+
+\noindent The GPT-2 responses are usually very lengthy and for the most part,
+the answer is not relevant to the question. To solve this problem, we chunked
+the answer into separate sentences and found the ones that are most
+\textit{semantically similar} to the question asked. For this task, we have
+tested and applied 4 different approaches:
 
@@
 
+\noindent Once the embeddings were generated, we have applied cosine similarity and in
+some cases, inner product and took 5 most similar sentences. Some additional
+regex and text filters were added for fixing punctuation and other grammar-related
+errors.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Questions}
+\section{Questions and Evaluation}
 
-For evaluating the performance of the approaches, we have chose 12 different
-questions. For each approach, we generated 5 different answers for the same
-question, resulting in the total of 240 answers. We then asked experienced
-medical personnel at Mayo Clinic to rate these answers. The questions are
-presented below.
+In order to evaluate the performance of the approaches as well as the overall
+performance of the chatbot, it was important to have the questions that both
+are frequently asked and linked to COVID-19. For this purpose, we decided to
+use 12 questions from the Kaggle's COVID-19 Open Research Dataset Challenge
+(CORD-19)~\cite{kaggle}. Most of the questions included a term ``COVID-19,''
+but some did not, in which case we appended the term to the end of the
+question. Figure 2 presents all 12 questions.
+
+\newpage % Needed to avoid unwanted spaces
+
+\begin{figure}[H]
+  \small
+  \begin{tabular}{p{0.1\linewidth}p{0.9\linewidth}}
+    \toprule
+    Number & Question\\
+    \midrule
+    \#1 & Are there geographic variations in the mortality rate of COVID-19?\\
+    \midrule
+    \#2 & What is known about transmission, incubation, and environmental
+      stability of COVID-19?\\
+    \midrule
+    \#3 & Is there any evidence to suggest geographic based virus mutations of
+      COVID-19?\\
+    \midrule
+    \#4 & Are there geographic variations in the rate of COVID-19 spread?\\
+    \midrule
+    \#5 & What do we know about virus genetics, origin, and evolution of
+      COVID-19?\\
+    \midrule
+    \#6 & What has been published about ethical and social science considerations
+      of COVID-19?\\
+    \midrule
+    \#7 & What has been published about medical care of COVID-19?\\
+    \midrule
+    \#8 & What do we know about diagnostics and surveillance of COVID-19?\\
+    \midrule
+    \#9 & What do we know about COVID-19 risk factors?\\
+    \midrule
+    \#10 & What has been published about information sharing and inter-sectoral
+      collaboration of COVID-19?\\
+    \midrule
+    \#11 & What do we know about vaccines and therapeutics of COVID-19\\
+    \midrule
+    \#12 & What do we know about non-pharmaceutical interventions of COVID-19?\\
+    \bottomrule
+  \end{tabular}
+  \caption{12 Questions from Kaggle.}
+\end{figure}
+
+\noindent For each approach, we generated 5 different answers for the same
+question, resulting in the total of 240 answers. Additionally, we made all of
+the answers publicly available on GitHub~\cite{github-results}. We then asked
+experienced medical personnel at Mayo Clinic to rate these answers. The rating
+system was composed of 5 different categories:
+
+\begin{figure}[H]
+  \small
+  \begin{tabular}{p{0.2\linewidth}p{0.7\linewidth}p{0.1\linewidth}}
+    \toprule
+    Category & Description & Point(s)\\
+    \midrule
+    Relevant & The answer partially or fully answers the question and/or
+      makes clear attempts to do so and is related to the question & 5\\
+    \midrule
+    Well-formed & the answer makes a logical sense and is somewhat related
+      to both the question and COVID-19, yet it does not (partially or
+      fully) answer the question & 4\\
+    \midrule
+    Informative & The answer is not related to the question, but provides
+        some information about COVID-19 and makes a logical sense & 3\\
+    \midrule
+    Acceptable & The answer makes some logical sense and is weakly related   to the question or COVID-19, but is mostly difficult to understand &
+      2\\
+    \midrule
+    Poor & the answer is totally unrelated to the question or COVID-19
+      and/or does not make a logical sense & 2\\
+    \bottomrule
+  \end{tabular}
+  \caption{5 Rating Categories.}
+\end{figure}
+
+\noindent Having 5 categories allowed for a flexibility of opinions and a broad range of scores which ultimately gave us a better way to evaluate
+our chatbot.
 
@@
 
+\subsection{General Performance.}
+
+\begin{figure}[H]
+  \small
+  \begin{tabular}{*{3}{c}}
+    \toprule
+    Annotator & Approach & Score\\
+    \midrule
+    \#1 & TfidfVectorizer + Cosine Similarity & 3.909\\
+    \midrule
+    \#2 & TfidfVectorizer + Cosine Similarity & 3.727\\
+    \midrule
+    Average & TfidfVectorizer + Cosine Similarity & 3.818\\
+    \midrule
+    \#1 & BERT + Cosine Similarity & 4.182\\
+    \midrule
+    \#2 & BERT + Cosine Similarity & 4.309\\
+    \midrule
+    Average & BERT + Cosine Similarity & 4.246\\
+    \midrule
+    \#1 & BioBERT + Cosine Similarity & 4.167\\
+    \midrule
+    \#2 & BioBERT + Cosine Similarity & 4.093\\
+    \midrule
+    Average & BioBERT + Cosine Similarity & 4.130\\
+    \midrule
+    \#1 & Universal Sentence Encoder (USE) + Inner Product & 3.696\\
+    \midrule
+    \#2 & Universal Sentence Encoder (USE) + Inner Product & 4.125\\
+    \midrule
+    Average & Universal Sentence Encoder (USE) + Inner Product & 3.911\\
+    \bottomrule
+  \end{tabular}
+  \caption{Comparison of 4 Different Approaches Across the Annotators.}
+\end{figure}
+
+\noindent The first annotator has rated BERT as the best approach with the
+average score of 3.909. BioBERT has shown roughly the same performance (4.167),
+with BERT rated slightly above. tf-idf procedure performed well, yet could not
+outperform neither BERT nor BioBERT. USE had the worst performance out of all
+embedding generation techniques with the score of 3.696 out of 5.
+
+\bigskip
+
+\noindent The second annotator, similarly, has given the highest average score
+to BERT (4.309). USE comes the second with the score of 4.125 followed by
+BioBERT with approximately the same score (4.093). tf-idf vectorization has
+yielded the worst results.
+
+\bigskip
+
+\noindent In general, the results show the consistency across the annotators.
+BERT and BioBERT have shown the best performance, with BERT being the leader.
+Their average scores were 4.246 and 4.130 respectively. tf-idf (3.818) and USE
+(3.911), on the other hand, have shown roughly similar, yet inferior to BERT
+and BioBERT, performance. All four approaches, on average, can be considered to
+be in the ``well-formed'' category with BERT and BioBERT being close to the
+``Relevant'' category.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Web Application
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Web Application}
+
+In order to make the chatbot more accessible to the general audience as well as
+for automating the response generation and facilitating information exchange,
+we have built a web application for the chatbot~\cite{web-app}. The application
+is powered by Python's flask~\cite{flask} package and gives a simple and
+user-friendly means for an interactive communication with the chatbot. In other
+words, any person could use this application to learn more about COVID-19 and
+get answers to their questions on this topic. The image below shows the web
+interface for the interactive chatbot.
+
 \begin{figure}[H]
   \centering
-  \begin{tabular}{*{2}{c}}
-    \toprule
-    Approach & Score\\
-    \midrule
-    TfidfVectorizer + Cosine Similarity & TBD\\
-    \midrule
-    BERT + Cosine Similarity & TBD\\
-    \midrule
-    BioBERT + Cosine Similarity & TBD\\
-    \midrule
-    Universal Sentence Encoder (USE) + Inner Product & TBD\\
-    \bottomrule
-  \end{tabular}
-  \caption{Comparison of 4 Different Approaches.}
+  \frame{\includegraphics[width=\linewidth]{webapp.png}}
+  \caption{An Image Depicting the Interactive Web Chatbot.}
 \end{figure}
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean porta purus et
-sem gravida rutrum. Maecenas blandit nulla ac luctus tempus. Nam finibus
-posuere ante, et lacinia massa vestibulum sit amet. Nulla velit arcu, efficitur
-quis turpis nec, sollicitudin lobortis nisi. Vivamus ut diam ut eros faucibus
-fringilla. Suspendisse pellentesque magna nec velit tristique sollicitudin.
-Morbi ultrices nec augue et molestie. Nam sapien ante, ullamcorper elementum
-convallis id, faucibus in lectus. Fusce pellentesque mollis velit efficitur
-porta. Sed finibus ligula quam, et lacinia velit posuere auctor. Donec ligula
-lorem, dictum nec lectus in, vehicula tincidunt massa. In hac habitasse platea
-dictumst.
+We have explored the feasibility of utilizing GPT-2 for answering questions
+related to COVID-19. GPT-2 was retrained on the CORD-19 corpus featuring
+thousands of scholarly articles. Some of the example answers to the
+COVID-19-related were made available online. Four different embedding
+generation techniques (tf-idf, BERT, BioBERT, and Universal Sentence Encoder
+(USE)) were compared.  The results were annotated by experienced medical staff
+at Mayo Clinic. The annotation results were consistent and concluded that BERT
+and BioBERT have the best average performance. USE came next with tf-idf
+showing the worst average performance.
 

### 2020-05-26 annotations/average_approach.py
Update repository

@@ -2,7 +2,7 @@
 # encoding: UTF-8
 
 """
-Filename: average.py
+Filename: average_approach.py
 Author:   David Oniani
 E-mail:   oniani.david@mayo.edu
 

### 2020-05-26 annotations/average_question.py

@@ -1,0 +1,251 @@
+#!/usr/bin/env python3
+# encoding: UTF-8
+
+"""
+Filename: average_question.py
+Author:   David Oniani
+E-mail:   oniani.david@mayo.edu
+
+Description:
+    Report average metrics.
+"""
+
+import numpy as np
+import pandas as pd
+
+
+def avg_question(df: pd.DataFrame, name: str) -> float:
+    return round(
+        (df.loc[df["Question"] == name]["Answer Relevance (1-5)"]).mean(), 3
+    )
+
+
+if __name__ == "__main__":
+    annotator_1 = pd.read_csv("annotator_1.csv")
+    annotator_2 = pd.read_csv("annotator_2.csv")
+
+    print("Annotator 1")
+    print("===========")
+
+    print(
+        "Are there geographic variations in the mortality rate of COVID-19?",
+        avg_question(
+            annotator_1,
+            "Are there geographic variations in the mortality rate of "
+            "COVID-19?",
+        ),
+    )
+
+    print(
+        "What is known about transmission, incubation, and environmental "
+        "stability of COVID-19?",
+        avg_question(
+            annotator_1,
+            "What is known about transmission, incubation, and environmental "
+            "stability of COVID-19?",
+        ),
+    )
+
+    print(
+        "Is there any evidence to suggest geographic based virus mutations of "
+        "COVID-19?",
+        avg_question(
+            annotator_1,
+            "Is there any evidence to suggest geographic based virus "
+            "mutations of COVID-19?",
+        ),
+    )
+
+    print(
+        "Are there geographic variations in the rate of COVID-19 spread?",
+        avg_question(
+            annotator_1,
+            "Are there geographic variations in the rate of COVID-19 spread?",
+        ),
+    )
+
+    print(
+        "What do we know about virus genetics, origin, and evolution of "
+        "COVID-19?",
+        avg_question(
+            annotator_1,
+            "What do we know about virus genetics, origin, and evolution of "
+            "COVID-19?",
+        ),
+    )
+
+    print(
+        "What has been published about ethical and social science "
+        "considerations of COVID-19?",
+        avg_question(
+            annotator_1,
+            "What has been published about ethical and social science "
+            "considerations of COVID-19?",
+        ),
+    )
+
+    print(
+        "What has been published about medical care of COVID-19?",
+        avg_question(
+            annotator_1,
+            "What has been published about medical care of COVID-19?",
+        ),
+    )
+
+    print(
[…]
